---
title: "Statistical Concepts"
author: "Sriramkumar Sarida"
---

> Load the data variable:

```{r}
random_vars <- readRDS("../../data/random_vars.rds")

View(random_vars)

random_vars
```

# Question 1

------------------------------------------------------------------------

For each variable, compute the following values. You can use the built-in functions or use the mathematical formulas.\
- expected value, variance, standard deviation

> computing the mean, variance and standard deviation

```{r}
# for Age
expected_value_age <- mean(random_vars$age)
variance_age <- var(random_vars$age)
standard_deviation_age <- sd(random_vars$age)

# for Income
expected_value_income <- mean(random_vars$income)
variance_income <- var(random_vars$income)
standard_deviation_income <- sd(random_vars$income)

```

> Printing mean, variance, standard deviation for age

```{r}

cat("# Expected Value:  =", expected_value_age)

cat("# Variance Value:  =", variance_age)

cat("# Standard Deviation Value:  =", standard_deviation_age)
```

> Printing mean, variance, standard deviation for Income

```{r}

cat("# Expected Value:  =", expected_value_income)

cat("# Variance Value:  =", variance_income)

cat("# Standard Deviation Value:  =", standard_deviation_income)
```

# Question 2

------------------------------------------------------------------------

**The standard deviations cannot be for atleast the provided dataset. The reason being, the variables assessed are age and income, which are measured in two different units and completely different scales. Therefore, it would not be ideal to compare these standard deviations.**

**The figures below are the plots of the Standard deviation of both Age and Income. We can see the scales and the distribution are completely different.**

```{r}
library(ggplot2)
ggplot(random_vars, aes(x = age)) +
  geom_histogram(binwidth = 1, fill = 'blue', alpha = 0.7) +
  geom_vline(aes(xintercept = expected_value_age), color = "red", linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = expected_value_age + standard_deviation_age), color = "red", size = 1) +
  geom_vline(aes(xintercept = expected_value_age - standard_deviation_age), color = "red", size = 1) +
  ggtitle("Distribution of Age with Standard Deviation")

# Plot for 'income'
ggplot(random_vars, aes(x = income)) +
  geom_histogram(binwidth = 100, fill = 'green', alpha = 0.7) +
  geom_vline(aes(xintercept = expected_value_income), color = "blue", linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = expected_value_income + standard_deviation_income), color = "blue", size = 1) +
  geom_vline(aes(xintercept = expected_value_income - standard_deviation_income), color = "blue", size = 1) +
  ggtitle("Distribution of Income with Standard Deviation")
```

# Question 3

Then, examine the relationship between both variables and compute:\
- covariance, correlation

```{r}
#Calculating Covariance and Correlation
covariance <- cov(random_vars$age, random_vars$income)
correlation <- cor(random_vars$age, random_vars$income)
```

> Printing covariance and correlation

```{r}

cat("# Covariance:  =", covariance)

cat("# Correlation:  =", correlation)

```

# Question 4

------------------------------------------------------------------------

**Correlation is a relatively easier measure to interpret. It is dimensionless and can provide information on the strength of the relationship between two variables, which makes it a perfect measure to compare Age and Income when these variables are fundamentally on two different scales. It is standardized to a range of -1 to 1, where the sign indicates the direction of the relationship, and the magnitude indicates the strength.**

*As the age increases, the income tends to increase as well, roughly accounting for 54.8%. This does not imply causation but there is a tendency for income to rise as the age rises.*

**On the other hand, Covariance is 29700.15. This value does not seem to be sensible between age and income. These variables have two different scales, which directly have an effect on the value of the Covariance.**

# Question 5

------------------------------------------------------------------------

Compute the conditional expected value for:\
- E\[income\|age \<= 18\]\
- E\[income\|age ∈ \[18, 65\]\]\
- E\[income\|age \>= 65\]

```{r}
expected_value_teens <- mean(random_vars$income[random_vars$age <= 18])
expected_value_adults <- mean(random_vars$income[random_vars$age > 18 & random_vars$age <= 65])
expected_value_seniors <- mean(random_vars$income[random_vars$age > 65])
```

> Printing covariance and correlation

```{r}

cat("# E[income|age <= 18]:  =", expected_value_teens)

cat("# E[income|age ∈ [18, 65]]:  =", expected_value_adults)

cat("# E[income|age >= 65]:  =", expected_value_seniors)

```
