---
title: "Regression and Statistical Inference"
author: "Sriramkumar Sarida"
---

# Read and check the dimensions

------------------------------------------------------------------------

> Load the data frame

```{r}
car_prices <- readRDS("../../data/car_prices.rds")
```

```{r}
dimensions <- dim(car_prices)

cat("# Dimensions of the dataframe:  =", dimensions)
```

# Use appropriate commands to get a more detailed look at the data

------------------------------------------------------------------------

```{r}
summary(car_prices)

str(car_prices)

head(car_prices)
```

**The data types are as follows: chr and num.**\
**The numeric data seems to be both decimal and whole numbers and they are classified under num. We can perform mathematical operations like summing, avergaing and so on.**\
**The strings are referred as *characters* data type. Operations like sorting, categorizing can be performed with this data type.**

# Run a linear regression. You want to explain what factors are relevant for the pricing of a car.

------------------------------------------------------------------------

```{r}
lm_model <- lm(price ~ ., data = car_prices)

summary(lm_model)
```

The number of '\*' indicates how significant the parameters are that affect the price of the car. From the table above, we can conclude that these factors play a significant role towards the price of the car:

-   **carbodyhardtop,**

-   **carbodyhatchback,**

-   **carbodywagon,**

-   **enginelocationrear,**

-   **carwidth,**

-   **enginetypeohc,**

-   **enginetypeohcv,**

-   **cylindernumberfive,**

-   **cylindernumberfour,**

-   **cylindernumbersix,**

-   **cylindernumbertwelve,**

-   **enginesize,**

-   **stroke,**

-   **peakrpm**

1.  *Both the R values are quite high, greater than 0.92, indicating that the model is biased.*

2.  *Additionally, the statistical significance for all the variables mentioned above are less than 0.05*

# Choosing **Regressor**

------------------------------------------------------------------------

I would like to choose the **Engine Size** as the regressor.

-   **Data type**: As we see from the summary of the linear regression, the data type of the **Engine Size** is **num** or a **numeric** value.

-   **Statistical Significance**: The p-value is 5.00e-06. It seems to be significantly smaller than 0.05, indicating that the effect it has on the **Price** is quite high.

-   **Effect it has on Price:** The coefficient of the **Engine Size is** 125.934. This value indicates that for each unit increase in size, the price is expected to increase by 125.934 units, keeping other variable constants.

# seat_heating

------------------------------------------------------------------------

```{r}
library(dplyr)
car_prices <- mutate(car_prices, seat_heating = TRUE)

lm_model_seat_heating <- lm(price ~ . + seat_heating, data = car_prices)

```

> Summary of the new model to see the coefficient of 'seat_heating'

```{r}
summary(lm_model_seat_heating)
```

From the table, we notice that the seat_heating has no impact on the price as the regressor model is unable to find any correlation between the price and seat_heating. Thats why the coefficient is NA. This could be due to the **Perfect Multi-Collinearity.** As the variable seat_heating is set to True and has no variation, the model cannot estimate a coefficient for it.
