---
title: "Causality"
author: "Sriramkumar Sarida"
---

# Famous example: Nicolas Cage films and number of poeple drowned by falling into a pool

------------------------------------------------------------------------

I came across this awful example of the number of people drowned by falling into a pool correlated with films Nicolas Cage appeared in during the same time period. I would like to recreate this example: https://www.datasciencecentral.com/wp-content/uploads/2021/10/2808309983.png

```{r}
set.seed(99)
years <- 2000:2009
cage_films <- cumsum(sample(1:5, 10, replace = TRUE))
drownings <- cumsum(sample(1:5, 10, replace = TRUE)) + rnorm(10, mean = 0, sd = 0.15)
data <- data.frame(Year = years, Cage_Films = cage_films, Drownings = drownings)

```

```{r}
data
```

```{r}
library(ggplot2)

ggplot(data, aes(x = Year)) + 
  geom_line(aes(y = Cage_Films, colour = "Nicolas Cage Films")) +
  geom_line(aes(y = Drownings, colour = "Drownings by falling into the pool")) +
  labs(title = "Spurious Correlation between Nicolas Cage Films and Drownings",
       y = "Count",
       colour = "Legend") +
  theme_minimal()


ggplot(data, aes(x = Cage_Films, y = Drownings)) +
  geom_point() +
  labs(title = "Scatter Plot of Nicolas Cage Films vs Drownings",
       x = "Nicolas Cage Films",
       y = "Drownings by falling into the pool") +
  theme_minimal()
```

-   The Line plot shows the the trend of number of films Nicolas Cage featured in over time and the number of drownings by falling into the pool. When I was generating random data for the drownings, I thought it made sense to add noise to the dataset.

-   The second plot shows the scatter plot showing this awful correlation.
