---
title: "Randomized Controlled Trials"
author: "Sriramkumar Sarida"
---

# Chatbot effect on E - Commerce Business

------------------------------------------------------------------------

## Load the data frame

```{r}
abtest_data  <- readRDS("../../data/abtest_online.rds")
```

```{r}
head(abtest_data)
```

> Plotting the abtest data to check the balance

```{r}
library(ggplot2)

compare_purchase <- 
  ggplot(abtest_data, aes(x = as.factor(chatbot), y = purchase, color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = FALSE) +
  labs(x = NULL, y = "Purchase", title = "Difference in purchase")


compare_purchase_amount <- 
  ggplot(abtest_data, aes(x = as.factor(chatbot), y = purchase_amount, color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = FALSE) +
  labs(x = NULL, y = "Purchase Amount", title = "Difference in purchase amount")
```

> Plot for purchase

```{r}
compare_purchase
```

> Plot for purchase amount

```{r}
compare_purchase_amount
```

## Run a regression to find the effect of chatbot on sales.

```{r}
lm_fit <- lm(purchase_amount ~ chatbot + previous_visit + mobile_device, data=abtest_data)
summary(lm_fit)
```

-   The **chatbot** variable seems to be having a negative impact on **purchase amount** with an estimate of -6.8488. This implies that the **chatbot** presence has decreased the sales and thereby reducing the **purchase amount**.

## Find subgroup-specific effects by including an interaction. Compute a CATE for one exemplary group. A subgroup could be for example mobile users.

```{r}
lm_cate <- lm(purchase_amount ~ chatbot * mobile_device + previous_visit, data=abtest_data)
summary(lm_cate)
```

## Binomial Outcome

```{r}
glm_fit <- glm(purchase ~ chatbot + previous_visit + mobile_device, family=binomial, data=abtest_data)
summary(glm_fit)
```

-   The estimated values from the logistic regression might not be as straightforward as linear regression, because the coefficients represent the change in logarithmic odds of the outcome for a unit change in the predictor variable.
